### 2019-03-05 paper/sex_selection_spacing-ver2.tex
Change to average spacing in tables and graphs

\input{../tables/bootstrap_duration_sex_ratio_low_all.tex}

@@

\input{../tables/bootstrap_duration_sex_ratio_med_all.tex}

@@

\input{../tables/bootstrap_duration_sex_ratio_high_all.tex}

>>>>

\input{../tables/bootstrap_duration_avg_sex_ratio_low_all.tex}

@@

\input{../tables/bootstrap_duration_avg_sex_ratio_med_all.tex}

@@

\input{../tables/bootstrap_duration_avg_sex_ratio_high_all.tex}
